1-generate-toys

### 2017-09-14 analysis/analyses/score_rules/1-generate-toys.Rmd
added grouping rule

```{r}
toys_blueprint <- tribble(
  ~generator_id, ~perturbator_id,
  "linear", "gs",
  "linear", "switch_two_cells",
  "linear", "switch_all_cells",
  "linear", "join_linear",
  "linear", "split_linear",
  "linear", "warp",
  "linear", "hairy",
  "linear", "hairy_small",
  "linear", "hairy_large",
  "linear", "remove_cells",
  "linear", "add_distant_edge",
  "linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  # bind_rows(tibble(generator_id="linear", perturbator_id=paste0("switch_", percs * 100))) %>% 
  rowwise() %>% 
  mutate(
  generator=list(get(paste0("generate_", generator_id))),
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)

>>>>

```{r}
toys_blueprint <- tribble(
  ~generator_id, ~perturbator_id,
  "linear", "gs",
  "linear", "switch_two_cells",
  "linear", "switch_all_cells",
  "linear", "join_linear",
  "linear", "split_linear",
  "linear", "warp",
  "linear", "hairy",
  "linear", "hairy_small",
  "linear", "hairy_large",
  "linear", "remove_cells",
  "linear", "add_distant_edge",
  "linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  bind_rows(tibble(generator_id="linear", perturbator_id=paste0("switch_", percs * 100))) %>%
  rowwise() %>% 
  mutate(
  generator=list(get(paste0("generate_", generator_id))),
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)
